---
title: "Online Cryptography Course Analysis"
author: "Angelo Sang"
date: "11/19/2021"
output: html_document
---


# ONLINE CRYPTOGRAPHY COURSE ANALYSIS
 
## Business Understanding
  Cryptography course was created by a Kenyan entrepreneur and would want to advertise it on her blog. She currently targets audiences originating from various countries. In the past, she ran ads to advertise a related course on the same blog and collected dat on the process. Using R programming language we would help her identify which individuals are most likely to click on her ads.

## Specifying the Data Analytic Question
  Use R Prigramming to identify which individuals are the most likely to click on the ads.

## Defining the Metric for Success
We identify the most important features for identifying which individuals are most likely to click on the ads.

## Recording the Experimental Design
1) Finding and dealing with outliers, anomalies and missing data within the dataset.
2) Performing univariate and Bivariate analysis

## Data Relevance
a) How accurate is the data at identifying which individuals are most likely to click on her ads?
b) Was the dataset sufficient?
c) Was the data biased?
d) Is the data source a reliable source?

```{r}
# loading the dataset and library
library(data.table)
df <- fread('http://bit.ly/IPAdvertisingData')

#previewing the dataset
print(head(df))
print(tail(df))
```
```{r}
# checking data types 
str(df)
```

## Cleaning the Dataset

```{r}
# checking for missing data
#is.na(df)
colSums(is.na(df))
#the data doesn't have missing data
```
```{r}
#checking the columns of the dataframe
colnames(df)
```

```{r}
# renaming the male column to gender
df2 <-rename(df, Gender = Male)
```

```{r}
# checking for duplicates 
#duplicated(df)
df[duplicated(df)]
```


```{r}

library(tidyverse)
# checking for outliers
boxplot(df$Age)
boxplot(df$`Area Income`)
boxplot(df$`Daily Internet Usage`)

# will not eliminate the outlies because the don't impact our analysis negatively
```

## UNIVARIATE ANALYSIS

```{r}
# Age column
# visualizing the age distribution using histogram
hist(df2$Age)

# there is a higher tendency that a person aged between 30 and 35 years of age accessed her ads.
```
```{r}
# visualizing the age distribution using bar graph
# fetching the age column
age <- df2$Age

# applying the table() function the compute the frequency of the Age column
age_frequency <- table(age)
age_frequency
```

```{r}
barplot(age_frequency)

# most people accessing her ads where aged 31 years
```
```{r}
# area_income
# visualizing the area_income distribution using histogram
hist(df2$`Area Income`)

#people leaving within an area_income between 60,000 and 65,000 had access on her ads the most
```
```{r}
# visualizing the daily_internet_usage distribution using histogram
hist(df2$`Daily Internet Usage`)
```
```{r}
# fetching the Gender column
gender <- df2$Gender

# applying the table() function to compute the frequency of the Gender column
gender_frequency <- table(gender)
gender_frequency

# 1 represented the males and 0 represented the females
```

```{r}
# visualizing the Gender distribution using bar graph
barplot(gender_frequency)

# most of the people who accessed her ads were females
```
```{r}
# Visualizing the number of people ho clicked on the ads using bar graph
# fetching the clicked on add column
clicked_on_ad <- df2$`Clicked on Ad`

#applying the table() function to compute the frequency of clicked on ad column
clicked_on_ad_frequency <- table(clicked_on_ad)
clicked_on_ad_frequency
```
 
```{r}
barplot(clicked_on_ad_frequency)

# half the number of people who had an access to her ads clicked on it.
```

## BIVARIATE ANALYSIS

```{r}
# Checking for covariance between area income and daily internet usage variables
#assigning the area income column to area_income variable
area_income <- df2$`Area Income`

#assigning the daily internet usage column to daily_internet_usage
daily_internet_usage <- df2$`Daily Internet Usage`

cov(are_income, daily_internet_usage)

#there is a positive linear relationship between the two variables
```

```{r}
# Checking for correlation coefficient between area income and daily internet usage variables
cor(area_income, daily_internet_usage)

# this indicates that there is a weak linear relationship between the two variables because their correlation coefficient is close to zero
```

```{r}

```







